ZCB Pricing

### 2018-08-05 ZCB Pricing .Rmd
fifa !!!!!
sensitivity plots update

senses <- matrix(nrow=13, ncol=9) # matrix to hold prices for various parameters
colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
xvec=c(Closed Form,Crude Monte Carlo,Antithetic Variates,Moment Matching,Control Variates,Explicit,Implicit,Crank Nicholson) #list of numerical methods

@@

plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[2,2:9], col="red",type = "p")
lines(1:8, senses[3,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("r=0.05", "r=0.08", "r=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

@@

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Variance")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[6,2:9], col="red",type = "p")
lines(1:8, senses[7,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

>>>>

senses <- matrix(nrow=13, ncol=9) # matrix to hold prices for various parameters
colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
#xvec=c(Closed Form,Crude Monte Carlo,Antithetic Variates,Moment Matching,Control Variates,Explicit,Implicit,Crank Nicholson) #list of numerical methods

@@

par(mfrow=c(1,1))
plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[2,2:9], col="red",type = "p")
lines(1:8, senses[3,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("r=0.05", "r=0.08", "r=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

@@

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[6,2:9], col="red",type = "p")
lines(1:8, senses[7,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
